---
title: "About"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r global-options, echo=FALSE}
# remove warning messages etc from final report
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
```

```{r results='hide'}
library(tidyverse)
library(targets)
```

# Setup

1.  Git clone or fork this repository.

2.  Place a `.Renviron` file in the root directory for this project, and complete the following details:

```{r}
tar_read(RENVIRON) %>% 
  readLines() %>%  
  purrr::map_chr(~ stringr::str_replace(string = .x, 
                                        pattern = "=.*$", 
                                        replacement = "=")) %>%  
  stringr::str_c(sep = "", 
                 collapse = "\n") %>% 
  cat()
```

3.  Update the workflowr website URL to match your own gitlab account details in `README.md` and `_site.yml`. Optionally, also rename the `.Rproj` file to something specific to your own dataset.

4.  Install required R packages with `renv::restore()`.

5.  Run targets pipeline with `targets::tar_make()`.
